### 2015-12-02 paper.tex
Clarify the role of blade BL transition

Mean rotor power and drag coefficients for multiple Reynolds numbers are plotted
versus tip speed ratio in Fig.~\ref{fig:cp-curves} and Fig.~\ref{fig:cd-curves},
respectively. $C_P$ is shown to increase in general with $Re$, along with a
reduction in the optimal tip speed ratio, due to the tendency of foils to stall at higher angles of attack at higher $Re$, and the higher angle of attack ranges seen by the blades at lower $\lambda$. These effects
diminish with increasing $Re$, which is expected as the blade boundary layers
transition from laminar to turbulent \textbf{\textit{[I wonder if this is relevant, since all cases are already in well in the turbulent regime]}} \cite{Lissaman1983,
Bachant2015-RVAT-Re-dep}. The rotor drag coefficient curves show similar
effects, but vary much less dramatically from each other.\textbf{\textit{[Overall I think we need more discussion for Figs 5 & 6.  For fig 5, maybe a discussion on stall delay and why Re independence is not achieve is sufficient.  Fig 6, need to find something to say, e.g. (1)why the trends look like that, is this expected? (2)Why they don't differ much between each other.    (3) mention that CD increases with ReD. ]}}

>>>>

Mean rotor power and drag coefficients for multiple Reynolds numbers are plotted
versus tip speed ratio in Fig.~\ref{fig:cp-curves} and Fig.~\ref{fig:cd-curves},
respectively. $C_P$ is shown to increase in general with $Re$, along with a
reduction in the optimal tip speed ratio, due to the tendency of foils to stall at higher angles of attack at higher $Re$, and the higher angle of attack ranges seen by the blades at lower $\lambda$. These effects
diminish with increasing $Re$, which is expected as the blade boundary layers
transition to turbulence closer to the leading edge \cite{Lissaman1983,
Bachant2015-RVAT-Re-dep}. The rotor drag coefficient curves show similar
effects, but vary much less dramatically from each other.\textbf{\textit{[Overall I think we need more discussion for Figs 5 & 6.  For fig 5, maybe a discussion on stall delay and why Re independence is not achieve is sufficient.  Fig 6, need to find something to say, e.g. (1)why the trends look like that, is this expected? (2)Why they don't differ much between each other.    (3) mention that CD increases with ReD. ]}}
